[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)

### 2020-02-22 analysis/paper.Rmd

# ==== Clean data
# Subset the GSS data to just the relevant fields for the relevant time frame, join, and recode the same way the 
  # original study does
study_data <- gss_all  %>%
  select(year, happy, race, marital) %>%
  filter(year <= 2012) %>%
  mutate(year = as.integer(year),
         happy = dplyr::recode(happy, `1`= 3L, `2` = 2L, `3` = 1L)) %>% #recode to increasing happiness from 1 to 3
  left_join(gini, by = c("year" = "year"))

>>>>

# ==== Clean data
# Subset the GSS data to just the relevant fields for the relevant time frame, join, and recode the same way the 
  # original study does
study_data <- gss_all  %>%
  select(year, happy, race, marital) %>%
  filter(year <= 2012) %>%
  mutate(year = as.integer(year),
         happy = dplyr::recode(as.integer(happy), `1`= 3L, `2` = 2L, `3` = 1L)) %>% #recode to increasing happiness from 1 to 3
  left_join(gini, by = c("year" = "year"))
